---
title: "MA [46]15 Homework 6"
author: "Daniel Sussman"
format: gfm
---

## Question 1

The code below loads in the `covid_data_count` tibble and processes it to 
change the counts from cumulative to semiweekly counts.

**[[**
For each of the comments numbered 1-4, answer the question about that line.
**]]**

```{r}
suppressPackageStartupMessages(library(tidyverse))

cdf <- 
  read_rds("covid_data_count.rds") |> 
  select(-Tests) |> 
  filter(race == "Total") |> 
  group_by(state) |>
    # 1. Why is the above line necessary for 2 to work?
  mutate(across(Cases:Hosp, \(v) v - lag(v, order_by = date))) |>
    # 2. What does the above line do?
  filter(if_all(Cases:Hosp, \(v) v >= 0)) |>
    # 3. What does the above line do?
  ungroup() |> 
  complete(state, date, race) |>
    # 4. What does the above line do?
  group_by(state, race)
```


## Question 2

**[[**
Create a new q2 where you make a scatter plot of the semi-weekly counts for deaths versus cases.
Remove the NAs beforehand to avoid any warnings.
Use transparency to avoid overplotting.
Make another plot showing deaths versus deaths/cases, again filtering 
observations beforehand to avoid warnings
Comment on if these look how you would expect.
**]]**


## Question 3

We hypothesize that the number of Cases is actually more predictive for future
weeks than for the current week. Here, we fit models for predicting `w` weeks
into the future for `w` = 0, 1, 2, 3, 4, and 5. We compare the models in terms
of the r-squared value to determine how many weeks into the future the number of
cases best predicts the number of deaths.

**[[**
In `q3a` below, modify the function `fit_lagged_model` as follows. The function
will first create a new column `lagged_cases` that has the number of cases
observed `w` weeks ago, recalling that there are 2 rows for each week. Fit a
model using `lm` with Deaths as the response variable and `lagged_cases` as the
predictor variable with no intercept. Take the results of that model and pipe
them into the last 3 lines of the function, leaving them as is. (You might need
to install the "broom" package.)
**]]**

```{r q3a}
fit_lagged_model <- function(w, covid_df){
  lm(x ~ y, data = tibble(x = 1:10, y = 2 * x + rnorm(10))) |> 
    broom::glance() |> 
    select(r.squared, sigma, nobs) |> 
    mutate(lag = w)
}
```

**[[**
After modifying the function, keep the `q3b` as is, run it, and observe the
output. In terms of `r.squared`, how many weeks into the future do Cases best
predict the number of deaths?
**]]**
```{r q3b}
map(seq(5), fit_lagged_model, covid_df = cdf) |> 
  list_rbind()
```

## Question 4

**[[**
Using your answer for the best number of weeks from Question 3, fit the same
model again and save the fitted model to a new variable in a new `q4` chunk. Use
`broom::tidy` on the fitted model to view a summary of the coefficient and its
statistics. Use `broom::augment` on the fitted model and make a plot of the
`.resid` versus `.fitted`. Interpret the values of the coefficients and comment
on the residual plot.
**]]**
